For Induction-Induction, Induction is Enough

### 2019-11-11 paper/paper.tex
infinitary IIT future work

\begin{itemize}
\item
  Finitary IIT signatures are obtained exactly by dropping equality constructors from
  finitary QIIT signatures. It follows that any model for the theory of QIIT signatures
  restricts to IITs, hence we inherit the categorical semantics of QIITs.
\item
  The term model construction also restricts in a straightforward way. For QIITs,
  term algebras are constructed by induction on the syntax of signatures, and
  then another induction constructs the eliminator (i.e.\ dependent induction
  principle). In both cases, simply dropping equality constructors from the
  induction yields restriction to IITs.
\end{itemize}

@@

Infinitary, explain why it is difficult. Without UIP, without funext,
for QIITs (in the setoid model).

>>>>

\begin{enumerate}
\item
  Finitary IIT signatures are obtained exactly by dropping equality constructors from
  finitary QIIT signatures. It follows that any model for the theory of QIIT signatures
  restricts to IITs, hence we inherit the categorical semantics of QIITs.
\item
  The term model construction also restricts in a straightforward way. For QIITs,
  term algebras are constructed by induction on the syntax of signatures, and
  then another induction constructs the eliminator (i.e.\ dependent induction
  principle). In both cases, simply dropping equality constructors from the
  induction yields restriction to IITs.
\end{enumerate}

@@

\subsection{Infinitary IITs}.

The current work only concerns finitary IITs. An extension would be to also
allow infinitely branching inductive types such as W-types. This would first
require giving semantics for infinitary IITs (to our knowledge there is no
previously published semantics that we can borrow), and also giving a term model
construction analogously to finitary QIITs. These steps seem feasible. However,
it seems to be more difficult to construct the syntax of infinitary IIT
signatures without using quotients. The reason is that such syntax would not be
strictly restricted to neutral terms: we would need $\lambda$-abstraction and
$\beta\eta$-rules for infinitary $\Pi$ types, in order to allow a term model
construction for infinitary IITs. A definition for normal preterms and typing
judgments on them may still be possible, but it appears to be much more
complicated than before (the current authors attempted this without conclusive
success).

\todo{Without UIP, without funext,
for QIITs (in the setoid model).}
